The effects of linkage disequilibrium on maintaining balanced polymorphisms in seasonal adaptation

### 2019-11-30 writing/manuscript.Rmd
figures

```{r global_options, include=FALSE}
knitr::opts_chunk$set(fig.pos = 'H',
                      fig.height = 3,
                      fig.width = 5)

require(tidyverse)
source(here::here("functions.R"))
```

@@

# plot the density distribution
ggplot(tbl_max_gen, aes(x = freqs, fill = filename)) +
  geom_density(alpha = 0.2) + 
  scale_fill_manual(values = c(rep("#e25dbb", 5), 
                               rep("#6cdf4c", 5),
                               rep("#258bd2", 5)),
                    breaks = unique(all_tbl$filename)[c(1,6,11)],
                    # legend name
                    name = "Epistasis",
                    # values tested
                    labels = c("0.5", "1", "2")) +
  ylab("Density") + 
  xlab("Allele Frequency") +
  theme_classic()

@@

# plot the density distribution
ggplot(tbl_max_gen, aes(x = freqs, fill = filename)) +
  geom_density(alpha = 0.2) + 
  scale_fill_manual(values = c(rep("#e25dbb", 5), 
                               rep("#6cdf4c", 5),
                               rep("#258bd2", 5)),
                    breaks = unique(all_tbl$filename)[c(1,6,11)],
                    # legend name
                    name = "Generations\nper year",
                    # values tested
                    labels = c("10", "20", "50")) +
  ylab("Density") + 
  xlab("Allele Frequency") +
  theme_classic()

@@

>>>>

```{r global_options, include=FALSE}
knitr::opts_chunk$set(fig.pos = 'H',
                      fig.height = 3,
                      fig.width = 6.5)

require(tidyverse)
require(cowplot)
source(here::here("functions.R"))
```

@@

# plot the density distribution
p1 <- ggplot(tbl_max_gen, aes(x = freqs, fill = filename)) +
        geom_density(alpha = 0.2) + 
        scale_fill_manual(values = c(rep("#e25dbb", 5), 
                                     rep("#6cdf4c", 5),
                                     rep("#258bd2", 5)),
                          breaks = unique(all_tbl$filename)[c(1,6,11)],
                          # legend name
                          name = "Epistasis",
                          # values tested
                          labels = c("0.5", "1", "2")) +
        ylab("Density") + 
        xlab("Allele Frequency") +
        theme_classic()

@@

# plot the density distribution
p2 <- ggplot(tbl_max_gen, aes(x = freqs, fill = filename)) +
        geom_density(alpha = 0.2) + 
        scale_fill_manual(values = c(rep("#e25dbb", 5), 
                                     rep("#6cdf4c", 5),
                                     rep("#258bd2", 5)),
                          breaks = unique(all_tbl$filename)[c(1,6,11)],
                          # legend name
                          name = "Generations\nper year",
                          # values tested
                          labels = c("10", "20", "50")) +
        ylab("Density") + 
        xlab("Allele Frequency") +
        theme_classic()

@@

```{r, fig.cap = 'Generations \\label{density_combined}', message = FALSE, echo = FALSE}
plot_grid(p1, p2, labels = "AUTO")
```
